\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-05-26 paper/ms.tex
response color [ci skip]

\newcommand{\response}[1]{{\color{green}#1}}

@@

In the following section, we present a method for substantially improving this
scaling in many circumstances.
We call our method and its implementations \celerite.\footnote{The name
\celerite\ comes from the French word \foreign{c\'elerit\'e} meaning the speed
of light in a vacuum.} The \celerite\ method requires using a specific model
for the covariance $k_\bvec{\alpha}(\bvec{x}_n,\,\bvec{x}_m)$ and, although it
has some limitations, we demonstrate in subsequent sections that it can
increase the computational efficiency of many astronomical data analysis
problems.
The main limitation of this method is that it can only be applied to
one-dimensional datasets, where by ``one-dimensional'' we mean that the
 \emph{input coordinates} $\bvec{x}_n$ are scalar, $\bvec{x}_n \equiv
t_n$.
We use $t$ as the input coordinate because one-dimensional GPs are often
applied to time series data but this isn't a real restriction and the
\celerite\ method can be applied to \emph{any} one-dimensional dataset.
Furthermore, the covariance function for the \celerite\ method is
``stationary''.
In other words, $k_\bvec{\alpha}(t_n,\,t_m)$ is only a function of $\tau_{nm}
\equiv |t_n - t_m|$.

>>>>

\newcommand{\response}[1]{{\color{blue}#1}}

@@

In the following section, we present a method for substantially improving this
scaling in many circumstances.
We call our method and its implementations \celerite.\footnote{The name
\celerite\ comes from the French word \foreign{c\'elerit\'e} meaning the speed
of light in a vacuum.
\response{Throughout the paper, when referring to the \celeriteterm\ model, we
typeset \celeriteterm\ in italics and, in reference to the implementation of
this model, we typeset \celerite\ in sans-serif.}}
The \celerite\ method requires using a specific model
for the covariance $k_\bvec{\alpha}(\bvec{x}_n,\,\bvec{x}_m)$ and, although it
has some limitations, we demonstrate in subsequent sections that it can
increase the computational efficiency of many astronomical data analysis
problems.
The main limitation of this method is that it can only be applied to
one-dimensional datasets, where by ``one-dimensional'' we mean that the
 \emph{input coordinates} $\bvec{x}_n$ are scalar, $\bvec{x}_n \equiv
t_n$.
We use $t$ as the input coordinate because one-dimensional GPs are often
applied to time series data but this isn't a real restriction and the
\celerite\ method can be applied to \emph{any} one-dimensional dataset.
Furthermore, the covariance function for the \celerite\ method is
``stationary''.
In other words, $k_\bvec{\alpha}(t_n,\,t_m)$ is only a function of $\tau_{nm}
\equiv |t_n - t_m|$.
